---
title: "r2anki-Notebook: snakecase package"
output:
  html_document:
    theme: "flatly"
    highlight: "pygments"
    self_contained: false  # false, so that images can be exported to anki as well
    toc: true
    toc_depth: 4
    toc_float: true
editor_options: 
  chunk_output_type: console
---
```{r, echo = FALSE}
knitr::opts_chunk$set(comment = "#>", collapse = TRUE)
```

<!-- #globaltags:  snakecase-pkg, strings -->

Please check https://github.com/Tazinho/snakecase to learn more!


******************
#### Snakecase: String Conversion 1
<!-- #tags: additional tags for this specific card -->
**How to convert the names of the iris dataset into snake case**

<!-- start backside --><br>
```{r}
snakecase::to_any_case(names(iris), case = "snake", preprocess = "\\.")
```
<!-- end backside -->


******************
#### Snakecase: String Conversion 2
<!-- #tags: additional tags for this specific card -->
**How to convert the following string into the desired output** 
```{r}
string <- c("BobDylanUSA",
            "MikhailGorbachevUSSR",
            "IAmATallDrinkOfWater")
```

```{r, eval = FALSE}
[1] "Bob Dylan USA"                 "Mikhail Gorbachev USSR"       "I Am A
Tall Drink Of Water"
```

<!-- start backside --><br>
```{r}
snakecase::to_any_case(string, case = "parsed", postprocess = " ")
```
<!-- end backside -->


******************
#### Snakecase: String Conversion 3
<!-- #tags: additional tags for this specific card -->
**How to convert this string into small camel case, with a dot as a separator?**
```{r}
string <- c("ICUDays","SexCode","MAX_of_MLD","Age.Group")
```

<!-- start backside --><br>
```{r}
snakecase::to_any_case(string, case = "small_camel", preprocess = "\\.", postprocess =
".")
```
<!-- end backside -->



******************
#### Snakecase: String Conversion 4
<!-- #tags: additional tags for this specific card -->
**How to convert the following string into snake case and leaving the decimal markers as they are?**
```{r}
string <- "R.Stüdio: v.1.0.143"
```

<!-- start backside --><br>
```{r}
snakecase::to_any_case(string, case = "snake",
            preprocess = ":|(?<!\\d)\\.",
            protect = "\\.")
```
<!-- end backside -->


******************
#### Snakecase: String Conversion 5
<!-- #tags: additional tags for this specific card -->
**How to convert the following string into snake case and replace every non alphanumeric character with an underscore?**
```{r}
string <- "R.Stüdio: v.1.0.143"
```

<!-- start backside --><br>
```{r}
snakecase::to_any_case(string, case = "snake",
            protect = "[^[:alnum:]]")
```
<!-- end backside -->


******************
#### Snakecase: String Conversion 6
<!-- #tags: additional tags for this specific card -->
**How to turn the following string into snake case?**
```{r}
string <- "HAMBURGCity"
```

<!-- start backside --><br>
```{r}
snakecase::to_any_case(string, case = "snake")
```
<!-- end backside -->
