---
title: "r2anki-Notebook: Dates and Times"
output:
  html_document:
    theme: "flatly"
    highlight: "pygments"
    self_contained: false  # false, so that images can be exported to anki as well
    toc: true
    toc_depth: 4
    toc_float: true
editor_options: 
  chunk_output_type: console
---
<!-- setup for selective highlighting -->
```{r, echo = FALSE}
knitr::opts_chunk$set(comment = "#>", collapse = TRUE)
```
```{r tdvs-highlight-setup, include=FALSE}
knitr::knit_hooks$set(source = function(x, options){
  str_class <- ifelse(is.null(options$class),
                      "",
                      paste0(".", options$class, collapse = " "))

  c(paste0("```{.r ", str_class, "}\n"),
    x,
    "\n```" )
}
)
```


Taken from https://github.com/Tazinho/Tidyverse-Cookbook.



# Dates and times

## Dates
******************
#### Dates 1
<!-- #tags: -->
**Convert a string into a date.**
<!-- start backside -->
```{r}
as.Date.character("2016-01-01") # also "2016/01/01" will work
```

```{r, class="tdvs"}
lubridate::ymd("2016-01-01") # also "2016/01/01", "20160101" and "2016:01:01" will work
```
<!-- end backside -->


******************
#### Dates 2
<!-- #tags: -->
**Add days (as an integer) to a date.**

<!-- start backside -->
```{r}
as.Date.character("2016-01-01") + 5
```

```{r, class = "tdvs"}
lubridate::ymd("2016-01-01") + 5
```
<!-- end backside -->


******************
#### Dates 3
<!-- #tags: -->
**Generate a (dense) sequence of days/weeks/months/years.**

<!-- start backside -->
```{r, class = "tdvs"}
lubridate::ymd("2016-01-01") + lubridate::days(0:3)
lubridate::ymd("2016-01-01") + lubridate::weeks(0:3)
lubridate::ymd("2016-01-01") + lubridate::month(0:3)
lubridate::ymd("2016-01-01") + lubridate::years(0:3)
lubridate::ymd("2012-01-01") + lubridate::dyears(1) # adds 365 days also for leap years
```
<!-- end backside -->


******************
#### Dates 4
<!-- #tags: -->
**Get the exact difference between two dates in days or other units:**

<!-- start backside -->
```{r}

```

```{r, class = "tdvs"}
as.double(difftime(lubridate::ymd_hms("2016-01-01 08:04:20"),
                   lubridate::ymd_hms("2016-04-01 12:03:00"),
                   units = "days"))
```
<!-- end backside -->


******************
#### Dates 5
<!-- #tags: -->
**Get the day of a week as an integer or as its name.**

<!-- start backside -->
```{r}

```

```{r, class = "tdvs"}
lubridate::wday("2016-01-01")
lubridate::wday("2016-01-01", label = TRUE)
```
<!-- end backside -->


******************
#### Dates 6
<!-- #tags: -->
**Get the day/month/year from a date.**

<!-- start backside -->
```{r}

```

```{r, class = "tdvs"}
lubridate::day("2016-01-01")
lubridate::week("2016-01-01")
lubridate::month("2016-01-01")
lubridate::month("2016-01-01", label = TRUE)
lubridate::year("2016-01-01")
```
<!-- end backside -->



******************
#### Dates 7
<!-- #tags: -->
**Get the last day of a month**

<!-- start backside -->
```{r}

```

```{r, class = "tdvs"}
last_day <- function(date) {
  lubridate::ceiling_date(date, "month") - lubridate::days(1)
  }
last_day(lubridate::ymd("2016-01-01"))
```
<!-- end backside -->


******************
#### Dates 8
<!-- #tags: -->
**Check if a year is a leap/non regular year:**
<!-- start backside -->
```{r}

```

```{r, class = "tdvs"}
lubridate::leap_year(2011)
```
<!-- end backside -->


## Dates and Times
******************
#### Convert to date-time (and set a specific timezone).
<!-- #tags: -->
** **

<!-- start backside -->
```{r}

```

```{r, class = "tdvs"}
lubridate::ymd_hms("2011-06-04 12:00:00", tz = "Pacific/Auckland")
```
<!-- end backside -->


******************
#### Dates and Times 1
<!-- #tags: -->
**Get the second/minute/hour from a date.**

<!-- start backside -->
```{r, class = "tdvs"}
lubridate::second(lubridate::ymd_hms("2011-06-04 12:00:00", tz = "Pacific/Auckland"))
lubridate::minute(lubridate::ymd_hms("2011-06-04 12:00:00", tz = "Pacific/Auckland"))
lubridate::hour(lubridate::ymd_hms("2011-06-04 12:00:00", tz = "Pacific/Auckland"))
```
<!-- end backside -->


******************
#### Dates and Times 2
<!-- #tags: -->
**Change the time depending on a timezone.**

<!-- start backside -->
```{r, class = "tdvs"}
meeting <- lubridate::ymd_hms("2011-07-01 09:00:00", tz = "Pacific/Auckland")
lubridate::with_tz(meeting, "America/Chicago")
```
<!-- end backside -->